Distributed Environment for Auctioning Virtual Power System Resources

### 2022-02-04 other/paper-aicts-chekan.tex
Update

The auction, as mentioned above, the module has become a prototype of the distributed environment. Being a part of a powerstand software, the module is used in educational institutions, engineering competitions, and intensive programs. During the powerstand operation and administration and personal observation of auction system operation, a significant amount of user experience was accumulated, based on decisions made regarding developing new versions of software products and creating unique technical solutions. This experience has become the primary source of expertise in forming requirements for a new interpretation of the auction system in distributed scenarios. Three events made the dominant contribution to the expertise. This section will describe them and briefly analyze the user experience.

@@

The rules of the event included practice games both in distributed and local formats. Local format implied the core services (incl. the auction module) to be placed in the stand instead of a cloud server. A service manager was implemented to set up and monitor applications based on a configuration file to perform mode switching. In practice, the service manager became a source of hard-to-diagnose bugs but still managed to complete the task.

>>>>

The aforementioned auction module has become a prototype of the distributed environment. Being a part of a powerstand software, the module is used in educational institutions, engineering competitions, and intensive programs. During the powerstand operation and administration and personal observation of auction system operation, a significant amount of user experience was accumulated, based on decisions made regarding developing new versions of software products and creating unique technical solutions. This experience has become the primary source of expertise in forming requirements for a new interpretation of the auction system in distributed scenarios. Three events made the dominant contribution to the expertise. This section will describe them and briefly analyze the user experience.

@@

The rules of the event included practice games both in distributed and local formats. Local format implied the core services (including the auction module) to be placed in the stand instead of a cloud server. A service manager was implemented to set up and monitor applications based on a configuration file to perform mode switching. In practice, the service manager became a source of hard-to-diagnose bugs but still managed to complete the task.
